Light inextensible strings under tension in the Schwarzschild geometry

### 2020-04-09 string_physics_teacher_revision.tex
revise for TPT as per issue #20

A light string's being under tension means that its path will be an
extremum of proper length.  In flat space, the calculus of variations
proves that the path is straight in the sense of zero curvature.  In
terrestrial gravity, standard $25\times
10^{-6}\unit{kg}\cdot\meter^{-1}$ cotton sewing thread at its breaking
strain of about $40\unit{N}$ would have a sag of~$\sim 6\times
10^{-6}\meter$ over a $1\meter$ horizontal scale: barely perceptible.
How does such a quotidian observation translate into the vicinity of a
black hole?  Would the ``warping of space'' result in {\em visibly}
curved thread?

>>>>

A light string's being under tension means that its path will be an
extremum of proper length.  In flat space, the calculus of variations
proves that the path is straight in the sense of zero curvature.  In
terrestrial gravity, standard $25\times
10^{-6}\unit{kg}\cdot\unit{m}^{-1}$ cotton sewing thread at its breaking
strain of about $40\unit{N}$ would have a sag of~$\sim 6\times
10^{-6}\unit{m}$ over a $1\unit{m}$ horizontal scale: barely perceptible.
How does such a quotidian observation translate into the vicinity of a
black hole?  Would the ``warping of space'' result in {\em visibly}
curved thread?
